---
title: "Sample Report"
author: "X.C."
date: "2024-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# My Summary of Today.

**This R workshop was so long but I learned something!** Overall, I had a great day but I am glad to be coming to the weekend.

## How I feel about Things.

*Thank goodness tomorrow is Friday.*

### Working with R is fun.

This is cool-looking code.

1.  It is relatively easy to use (?)
2.  It provides lots of functionality for data vis.
3.  My lab partners all use it.

-   thing 1

-   thing 2

-   thing 3

[Center for Teaching Excellence](https://cte.rice.edu)

### Loading Data and packages

```{r load_data and packages, echo= FALSE, results= "hide", message=FALSE, warning=FALSE}
gapminder <- read.csv("data/gapminder_data.csv", 
                      stringsAsFactors = TRUE)
library(ggplot2)
library(dplyr)
```

### Basic Plots

```{r plot_data}
ggplot(data = gapminder, 
       mapping = aes(x = pop, y = lifeExp)) + 
  geom_point(alpha = 0.3, color = 'salmon')
```

Add code in the markdown. It provides the output in the document. `r 2 + 2`

```{r variable_definition, echo = FALSE, results= "hide"}
US_2007 <- gapminder %>% 
  filter(country == "United States", year == 2007)
options(scipen = 999)
```

The 2007 us gross domestic product per capital is `r US_2007$gdpPercap`. 
